Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-09-14 ms.tex
clarified the optical depth in the high res spectrum and also turned on track changes.

% manuscript produces a one-column, double-spaced document:
%\documentclass[12pt,preprint]{aastex}
\documentclass[preprint]{aastex61}
%\documentclass[iop]{emulateapj}

@@

We summarize these \texttt{SpecMatch-Emp} and BOSZ results in Table \ref{tab:stellObsParams}, which both favor a main-sequence log(g) $\approx$ 4.6 star.
Our analysis of the median 2015 spectrum therefore indicates that the stellar spectrum shows no strong contamination from planet disintegration activity.
Unfortunately, this makes diagnosing the gaseous material evaporating from sublimated dust grains challenging to detect.
A brighter transiting disintegrating system may reveal itself more strongly, if discovered in the TESS field.

@@

\citet{vanlieshout2016kic1255} compiled the stellar parameters reported in the literature via photometric and spectroscopic methods and note that the high resolution spectrum show that \shStar\ has the gravity of a sub-giant, whereas all other methods find that it is a main sequence star.
One exciting possibility suggested in \citet{vanlieshout2016kic1255} is that the planet disintegration affects the spectral lines of the star and affects the high resolution spectrum from \citet{kawahara2013starspots}.
We explore this possibility by examining archival Subaru HDS spectra of \shStar.
We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_{eff}$=4440 $\pm$ 70 K, log(g) = 4.63 $\pm$ 0.12, [Fe/H]=-0.08$\pm$0.09, M=0.69$\pm$0.10 R$_\odot$ and M=0.70 $\pm$0.08 M$_\odot$.
Therefore, the optical depth of any gas sublimating off dust grains is too small to affect the high resolution spectrum.
We argue that low signal to noise in the initial Subaru HDS spectra affected previous interpretations of the stellar parameters.

>>>>

% manuscript produces a one-column, double-spaced document:
%\documentclass[12pt,preprint]{aastex}
\documentclass[preprint,trackchanges]{aastex61}
%\documentclass[iop]{emulateapj}

@@

We summarize these \texttt{SpecMatch-Emp} and BOSZ results in Table \ref{tab:stellObsParams}, which both favor a main-sequence log(g) $\approx$ 4.6 star.
Our analysis of the median 2015 spectrum therefore indicates that the stellar spectrum shows no strong contamination from planet disintegration activity \added{at the level where it would affect the derived stellar parameters}.
Unfortunately, this makes diagnosing the gaseous material evaporating from sublimated dust grains challenging to detect.
A brighter transiting disintegrating system may reveal itself more strongly, if discovered in the TESS field.

@@

\citet{vanlieshout2016kic1255} compiled the stellar parameters reported in the literature via photometric and spectroscopic methods and note that the high resolution spectrum show that \shStar\ has the gravity of a sub-giant, whereas all other methods find that it is a main sequence star.
One exciting possibility suggested in \citet{vanlieshout2016kic1255} is that the planet disintegration affects the spectral lines of the star and affects the high resolution spectrum from \citet{kawahara2013starspots}.
We explore this possibility by examining archival Subaru HDS spectra of \shStar.
We find that the high resolution spectra are consistent with previous photometry and spectroscopy and that the host star is on the main sequence with T$_{eff}$=4440 $\pm$ 70 K, log(g) = 4.63 $\pm$ 0.12, [Fe/H]=-0.08$\pm$0.09, M=0.69$\pm$0.10 R$_\odot$ and M=0.70 $\pm$0.08 M$_\odot$.
Therefore, the optical depth of any gas sublimating \replaced{of}{off} dust grains is too small to affect \added{the parameters derived from} the high resolution spectrum.
We argue that low signal to noise in the initial Subaru HDS spectra affected previous interpretations of the stellar parameters.
